Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
update files

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Read and prepare data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

* Two datasets: focal tree and competence 
```{r}
# Compute diameter (mm)
tree <- tree %>% 
  mutate(dn_mm = (perim_mm / pi))

@@

# General Variables 
```{r}
general_var <- ft %>% group_by(loc, site) %>% count()

@@

# Spatial Info
```{r, spatialData} 
## Get coordinates of spatial data  
sp_ca <- as.data.frame(field_work_ca) %>% 
  dplyr::select(ele, name, lat = coords.x2, long = coords.x1)

@@

# Competition data
```{r}
# Read competition
compe <- read.csv(file=paste(di, "/data/competence/competence_indices.csv", sep=""), header=TRUE, sep=',')

@@

#### Function to comparison (aov)
```{r}
compara <- function(df, mivariable){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest

@@

## Comparison

```{r}

# Select only variables to compare 
compe_sel <- compe %>% dplyr::select(ba:dnn,site)

@@

## Distance-Independet Indices 
### Basal Area
```{r}
mivariable <- 'ba'
s <- get(paste0('aov_', mivariable))

>>>>

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Prepare Data
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

* Two datasets: focal tree and competence

```{r}
# Compute diameter (mm)
tree <- tree %>% 
  mutate(dn_mm = (perim_mm / pi))

@@

# General Variables 
Numbers of focal trees by site

```{r}
general_var <- ft %>% group_by(loc, site) %>% count()

@@

# Spatial Info
Coordinates of the centroid for each site

```{r, spatialData} 
## Get coordinates of spatial data  
sp_ca <- as.data.frame(field_work_ca) %>% 
  dplyr::select(ele, name, lat = coords.x2, long = coords.x1)

@@

# Competition data

* Read data 
```{r, echo=FALSE}
# Read competition
compe <- read.csv(file=paste(di, "/data/competence/competence_indices.csv", sep=""), header=TRUE, sep=',')

@@

* Create a custom function to compare between sites (aov & post hoc)

```{r, echo=FALSE}
#### Function to comparison (aov)
compara <- function(df, mivariable){ 
  require('dplyr')
  require('multcomp')
  require('broom') 
  # mivariable: variabe of interest

@@

* Export data into text files (see `/out/anovas_competition/`)

```{r, echo=FALSE}
## Comparison 
# Select only variables to compare 
compe_sel <- compe %>% dplyr::select(ba:dnn,site)

@@

## Distance-Independet Indices 
### Basal Area
```{r, echo=FALSE}
mivariable <- 'ba'
s <- get(paste0('aov_', mivariable))
